### 2018-08-07 paper/system-model.tex

The use of the cloud provider, as a third party,
provides two main privacy properties, which we should preserve when
moving to a P2P~\cite{DevilInMetadata} setting:
\begin{itemize}
\item Alice and Bob are the only users who learn 
about Alice sharing a file with Bob.
\item The composition and behavior of Alice and Bob's \squad remain
  hidden to each other, and to other users. I.e. Alice does not learn
  which devices Bob owns or uses, let alone how Bob uses them, and
  reciprocally.
\end{itemize} 
The cloud provider, however, has this information and any other
stemming from the users' interaction with the service, and can draw
inferences from metadata even when the data itself is encrypted. The
provider thus poses a threat to the users' privacy which we remove in
the P2P scenario.

@@

Friendly surveillance can be mitigated by ensuring security properties 
typically associated with onion routing, as defined by Camenisch and Lysyanskaya~\cite{CLOnionRouting}: 
% We combine the requirements from
% the \ac{P2P} setting with those from onion routing for anonymity.
% Camenisch and Lysianskaya \cite{CLOnionRouting} define security properties 
% for onion routing:
onion-correctness, integrity, and security %(wrap resistance,
                                %indistinguishability). 
Informally, onion-correctness means that if an onion is formed
correctly, processed by the correct routers in the correct order, then
the correct message is received by the last router. Onion-integrity
means that even for an onion created by an adversary, the path length
is bounded by $N$. Onion-security means that an adversary sending a
challenge onion to a router and able to see the outcome of how the
onion is processed, cannot distinguish between whether that onion
corresponds to a particular message and route or not. This is also
true for a \emph{re-wrapped} onion, i.e. a challenge onion wrapped in
another layer. The formal definitions are in~cite{CLOnionRoutin} along
with a theorem that states that an onion routing scheme satisfying
these three properties, combined with secure point-to-point channels,
is UC-secure.

@@

 \commentFT{Removed, as did not fit with
  the flow, but probably needed somewhere: `We give the definitions
  for the security and privacy properties of \name in
  Section~\ref{security-discussion}.'} \sonja{better here. Need to define
  device unlinkability, the rest is covered by Camenisch.}

>>>>

The use of the cloud provider, as a third party,
provides two main privacy properties, which we should preserve when
moving to a P2P setting:
\begin{itemize}
\item Alice and Bob are the only users who learn 
about Alice sharing a file with Bob.
\item The composition and behavior of Alice and Bob's \squad remain
  hidden to each other, and to other users. I.e. Alice does not learn
  which devices Bob owns or uses, let alone how Bob uses them, and
  reciprocally.
\end{itemize} 
The cloud provider, however, has this information and any other
stemming from the users' interaction with the service, and can draw
inferences from metadata even when the data itself is encrypted. The
provider thus poses a threat to the users' privacy which we remove in
the P2P scenario~\cite{DevilInMetadata}.

@@

Friendly surveillance can be mitigated by ensuring security properties 
typically associated with onion routing, as defined by Camenisch and Lysyanskaya~\cite{CLOnionRouting}: 
% We combine the requirements from
% the \ac{P2P} setting with those from onion routing for anonymity.
% Camenisch and Lysianskaya \cite{CLOnionRouting} define security properties 
% for onion routing:
onion-correctness, integrity, and security %(wrap resistance,
                                %indistinguishability). 
Informally, onion-correctness means that if an onion is formed
correctly, processed by the correct routers in the correct order, then
the correct message is received by the last router. Onion-integrity
means that even for an onion created by an adversary, the path length
is bounded by $N$. Onion-security means that an adversary sending a
challenge onion to a router and able to see the outcome of how the
onion is processed, cannot distinguish between whether that onion
corresponds to a particular message and route or not. This is also
true for a \emph{re-wrapped} onion, \ie a challenge onion wrapped in
another layer. The formal definitions are in~\cite{CLOnionRouting} along
with a theorem that states that an onion routing scheme satisfying
these three properties, combined with secure point-to-point channels,
is UC secure.

@@

 % \commentFT{Removed, as did not fit with
 %  the flow, but probably needed somewhere: `We give the definitions
 %  for the security and privacy properties of \name in
 %  Section~\ref{security-discussion}.'} \sonja{better here. Need to define
 %  device unlinkability, the rest is covered by Camenisch.}
